---
title: "<a href = 'https://adventofcode.com/2023'> Advent of Code 2023 </a>"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, collpase = TRUE, out.width = "100%")
```

# Summary

Advent of Code is an annual event which consists of daily programming puzzles.
The event is hosted by [Eric Wastl](http://was.tl/) and takes place between December 1st and December 25th.

I solved all puzzles using R (version 4.3.1.) Most of the solutions only require base packages.
For Days 08 and 20 I borrowed the function `Lcm` from the `pracma` package.

For Day 17 I used the `collections` library which provides high performance container types (in particular priority queues).

I try to go for fast and short (sometimes a bit hackey) solutions which means that the resulting 
code is not always as easy to read as it could be.


```{r, echo = FALSE, message=FALSE, warning= FALSE, fig.width=10, fig.height=10}
library(tidyverse)

print(readRDS("Output/AoC2023_results.RDS"))
```

